---
title: "New data"
author: "Ziqi Zhou"
date: "11/13/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(curl)
library(lubridate)

library(shiny)
library(DT)
library(patchwork)

library(readxl)
library(sp)
library(tmap)  
library(viridis)
library(leaflet)
library(tigris)
library(plotly)
library(shinyWidgets)
library(table1)
library(htmlTable)
library(scales)

library(RColorBrewer)
library(grid)


library(Dict)
library(lubridate)
```

```{r}
test_trend = read.csv(curl("https://raw.github.com/nychealth/coronavirus-data/master/trends/tests.csv")) %>% janitor::clean_names()

#write_csv(test_trend,"test_trend.csv")

#test.trend = read.csv("/Users/ziqizhou/Downloads/tests.csv") %>% 
#  janitor::clean_names() 

#day = c(as.Date("2020-03-20"):as.Date("2020-11-09"))
#day = as.Date(day, origin = "1969-12-15")
```

```{r}

ggplot(test_trend, aes(x = as.Date(date), y = total_tests)) + 
  geom_col(color = "#F6BDBC", fill = "#F6BDBC", alpha = 0.8) + 
  geom_line(aes(x = as.Date(date), y = total_tests_7days_avg), color = "red", size = 1) + 
  ggtitle("New tests by day in New York City") + 
  theme_classic() + 
  theme(
    axis.title.x = element_blank(),
    axis.title.y = element_blank(),
    plot.title = element_text(hjust = 0, size = 14)
  )
```

## Number of people with a positive result on a PCR test
```{r}

ggplot(test_trend, aes(x = as.Date(date), y = positive_tests
)) + 
  geom_col(color = "#F6BDBC", fill = "#F6BDBC", alpha = 0.8) + 
  geom_line(aes(x = as.Date(date), y = positive_tests_7days_avg), color = "red", size = 1) + 
  ggtitle("New tests by day in New York City") + 
  theme_classic() + 
  theme(
    axis.title.x = element_blank(),
    axis.title.y = element_blank(),
    plot.title = element_text(hjust = 0, size = 14)
  )
```
## Percentage of people tested with a PCR test who tested positive

```{r}
ggplot(test_trend, aes(x = as.Date(date), y = percent_positive)) + 
  geom_col(color = "#F6BDBC", fill = "#F6BDBC", alpha = 0.8) + 
  geom_line(aes(x = as.Date(date), y = percent_positive_7days_avg), color = "red", size = 1) + 
  ggtitle("New tests by day in New York City") + 
  theme_classic() + 
  theme(
    axis.title.x = element_blank(),
    axis.title.y = element_blank(),
    plot.title = element_text(hjust = 0, size = 14)
  )
```


# draw a antibody test map

COVID-19 Antibody Tests by NYC ZIP Code Tabulation Areas (ZCTAs)

This map may be used to visualize how COVID-19 antibody tests vary by NYC ZCTAs. Select available display options to visualize the data. Click a ZCTA on the map to see the data. These data are updated daily.

```{r}
spdf = rgdal::readOGR("./Geography-resources/MODZCTA_2010_WGS1984.geo.json")

antibody = read.csv(curl("https://raw.github.com/nychealth/coronavirus-data/master/totals/antibody-by-modzcta.csv")) 
#write_csv(antibody,paste0("antibody_zcta",month(today),day(today),".csv"))
antibody = antibody %>% janitor::clean_names()
```

```{r antibody_percent_posit}
data_to_plot = antibody
  data_to_plot_geo = geo_join(spdf,data_to_plot,"MODZCTA","modzcta_first")
  data_to_plot_geo = subset(data_to_plot_geo, !is.na(percent_positive))
  pal <- colorNumeric("Reds", domain=data_to_plot_geo$percent_positive)
  
  popup_sb <- paste0("Neighborhood Name: ", as.character(data_to_plot_geo$neighborhood_name),
                     "<br>", 
                     "MODZCTA: ", as.character(data_to_plot_geo$modzcta_first),
                     "<br>", 
                     "Death Rate of COVID-19: ", as.character(data_to_plot_geo$percent_positive)
  )
  
  p1 = leaflet() %>%
    addProviderTiles("CartoDB.Positron") %>%
    setView(lng = -73.99653, lat = 40.75074, zoom = 10) %>% 
    addPolygons(data =  data_to_plot_geo , 
                fillColor = ~pal(data_to_plot_geo$percent_positive), 
                fillOpacity = 0.7, 
                weight = 0.2, 
                smoothFactor = 0.2, 
                popup = ~popup_sb) %>%
    addLegend(pal = pal, 
              values =  data_to_plot_geo$percent_positive, 
              position = "bottomright", 
              title = "Number")
  p1
```

```{r antibody_num_posit}
data_to_plot = antibody
  data_to_plot_geo = geo_join(spdf,data_to_plot,"MODZCTA","modzcta_first")
  data_to_plot_geo = subset(data_to_plot_geo, !is.na(num_peop_pos))
  pal <- colorNumeric("Reds", domain=data_to_plot_geo$num_peop_pos)
  
  popup_sb <- paste0("Neighborhood Name: ", as.character(data_to_plot_geo$neighborhood_name),
                     "<br>", 
                     "MODZCTA: ", as.character(data_to_plot_geo$modzcta_first),
                     "<br>", 
                     "Death Rate of COVID-19: ", as.character(data_to_plot_geo$num_peop_pos)
  )
  
  p2 = leaflet() %>%
    addProviderTiles("CartoDB.Positron") %>%
    setView(lng = -73.99653, lat = 40.75074, zoom = 10) %>% 
    addPolygons(data =  data_to_plot_geo , 
                fillColor = ~pal(data_to_plot_geo$num_peop_pos), 
                fillOpacity = 0.7, 
                weight = 0.2, 
                smoothFactor = 0.2, 
                popup = ~popup_sb) %>%
    addLegend(pal = pal, 
              values =  data_to_plot_geo$num_peop_pos, 
              position = "bottomright", 
              title = "Number")
  p2
```

