---
title: "data clean routine"
author: "Ziqi Zhou"
date: "8/17/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Tracker Data
```{r}
### trakcer data
data_yester = read_csv("./data/data-by-modzcta0722.csv") %>% 
  janitor::clean_names() %>% 
  mutate(date = as.Date("2020-07-22"))
data_today = read_csv("./data/data-by-modzcta0723.csv") %>% 
  janitor::clean_names() %>% 
  mutate(date = as.Date("2020-07-23"))

data = rbind(data_today,data_yester)
new_case = 0
new_death = 0

for (i in 1:177) {
  new_case[i] = data[i,4] - data[i+177,4]
  new_case
  
  new_death[i] = data[i,7] - data[i+177,7]
  new_death
}

for (i in 178:354) {
  
  new_case[i] = NA
  
  new_death[i] = NA
}

data_to_table = data %>% 
  mutate(new_case = new_case,
         new_death = new_death) %>% 
  filter(date == max(date)) %>% 
  mutate(new_case = as.numeric(new_case),
         new_death = as.numeric(new_death),
         incidence_rate = round(new_case*100000/pop_denominator, digits = 1) )%>% 
  dplyr::select(modified_zcta,neighborhood_name,borough_group,
                covid_case_count,new_case,incidence_rate,
                covid_death_count,new_death, total_covid_tests) %>% 
  rename("New Cases" = new_case,
         "New Deaths" = new_death,
         Zipcode = modified_zcta,
         "Neighborhood" = neighborhood_name,
         "Borough"= borough_group,
         "Case Count" = covid_case_count,
         "Death Count" = covid_death_count,
         "Incidence Rate (Per 100,000 people)" = incidence_rate,
         "Total COVID-19 Tests" = total_covid_tests )
```

## Distribution Tab Map
```{r}
data_to_plot = data %>% 
  mutate(new_case = new_case,
         new_death = new_death
  ) %>% 
  filter(date == max(date)) %>% 
  mutate(new_case = as.numeric(new_case),
         new_death = as.numeric(new_death),
         incidence_rate = round(new_case*100000/pop_denominator, digits = 1) )

```

### COVID-19 by demo
*by age*
We also have data by sex and by race but the codes are the same we just need to change the name and the path of the files. You could find the in the '/data_covid_demo/' folder.
```{r, include=FALSE,message=FALSE,warning=FALSE}
#read the data

byage0518 = read_csv("./data/data_covid_demo/boros_by_age/boroughs-by-age0518.csv") %>% 
  pivot_longer(BK_CASE_COUNT:SI_DEATH_RATE,
               names_to = "location_n_event",
               values_to = "count")%>% 
  mutate(day = "2020-05-18",
         day = as.Date(day))

byage0519 = read_csv("./data/data_covid_demo/boros_by_age/boroughs-by-age0519.csv") %>% 
  pivot_longer(BK_CASE_COUNT:SI_DEATH_RATE,
               names_to = "location_n_event",
               values_to = "count")%>% 
  mutate(day = "2020-05-19",
         day = as.Date(day))
byage0520 = read_csv("./data/data_covid_demo/boros_by_age/boroughs-by-age0520.csv") %>% 
  pivot_longer(BK_CASE_COUNT:SI_DEATH_RATE,
               names_to = "location_n_event",
               values_to = "count")%>% 
  mutate(day = "2020-05-20",
         day = as.Date(day))
byage0521 = read_csv("./data/data_covid_demo/boros_by_age/boroughs-by-age0521.csv") %>% 
  pivot_longer(BK_CASE_COUNT:SI_DEATH_RATE,
               names_to = "location_n_event",
               values_to = "count")%>% 
  mutate(day = "2020-05-21",
         day = as.Date(day))
byage0522 = read_csv("./data/data_covid_demo/boros_by_age/boroughs-by-age0522.csv") %>% 
  pivot_longer(BK_CASE_COUNT:SI_DEATH_RATE,
               names_to = "location_n_event",
               values_to = "count")%>% 
  mutate(day = "2020-05-22",
         day = as.Date(day))
byage0523 = read_csv("./data/data_covid_demo/boros_by_age/boroughs-by-age0523.csv") %>% 
  pivot_longer(BK_CASE_COUNT:SI_DEATH_RATE,
               names_to = "location_n_event",
               values_to = "count")%>% 
  mutate(day = "2020-05-23",
         day = as.Date(day))
byage0524 = read_csv("./data/data_covid_demo/boros_by_age/boroughs-by-age0524.csv") %>% 
  pivot_longer(BK_CASE_COUNT:SI_DEATH_RATE,
               names_to = "location_n_event",
               values_to = "count")%>% 
  mutate(day = "2020-05-24",
         day = as.Date(day))
byage0525 = read_csv("./data/data_covid_demo/boros_by_age/boroughs-by-age0525.csv") %>% 
  pivot_longer(BK_CASE_COUNT:SI_DEATH_RATE,
               names_to = "location_n_event",
               values_to = "count")%>% 
  mutate(day = "2020-05-25",
         day = as.Date(day))
byage0526 = read_csv("./data/data_covid_demo/boros_by_age/boroughs-by-age0526.csv") %>% 
  pivot_longer(BK_CASE_COUNT:SI_DEATH_RATE,
               names_to = "location_n_event",
               values_to = "count")%>% 
  mutate(day = "2020-05-26",
         day = as.Date(day))
byage0527 = read_csv("./data/data_covid_demo/boros_by_age/boroughs-by-age0527.csv") %>% 
  pivot_longer(BK_CASE_COUNT:SI_DEATH_RATE,
               names_to = "location_n_event",
               values_to = "count")%>% 
  mutate(day = "2020-05-27",
         day = as.Date(day))
byage0528 = read_csv("./data/data_covid_demo/boros_by_age/boroughs-by-age0528.csv") %>% 
  pivot_longer(BK_CASE_COUNT:SI_DEATH_RATE,
               names_to = "location_n_event",
               values_to = "count")%>% 
  mutate(day = "2020-05-28",
         day = as.Date(day))
byage0529 = read_csv("./data/data_covid_demo/boros_by_age/boroughs-by-age0529.csv") %>% 
  pivot_longer(BK_CASE_COUNT:SI_DEATH_RATE,
               names_to = "location_n_event",
               values_to = "count")%>% 
  mutate(day = "2020-05-29",
         day = as.Date(day))
byage0530 = read_csv("./data/data_covid_demo/boros_by_age/boroughs-by-age0530.csv") %>% 
  pivot_longer(BK_CASE_COUNT:SI_DEATH_RATE,
               names_to = "location_n_event",
               values_to = "count")%>% 
  mutate(day = "2020-05-30",
         day = as.Date(day))
byage0531 = read_csv("./data/data_covid_demo/boros_by_age/boroughs-by-age0531.csv") %>% 
  pivot_longer(BK_CASE_COUNT:SI_DEATH_RATE,
               names_to = "location_n_event",
               values_to = "count")%>% 
  mutate(day = "2020-05-31",
         day = as.Date(day))

byage0601 = read_csv("./data/data_covid_demo/boros_by_age/boroughs-by-age0601.csv") %>% 
  pivot_longer(BK_CASE_COUNT:SI_DEATH_RATE,
               names_to = "location_n_event",
               values_to = "count")%>% 
  mutate(day = "2020-06-01",
         day = as.Date(day))
byage0602 = read_csv("./data/data_covid_demo/boros_by_age/boroughs-by-age0602.csv") %>% 
  pivot_longer(BK_CASE_COUNT:SI_DEATH_RATE,
               names_to = "location_n_event",
               values_to = "count")%>% 
  mutate(day = "2020-06-02",
         day = as.Date(day))
byage0603 = read_csv("./data/data_covid_demo/boros_by_age/boroughs-by-age0603.csv") %>% 
  pivot_longer(BK_CASE_COUNT:SI_DEATH_RATE,
               names_to = "location_n_event",
               values_to = "count")%>% 
  mutate(day = "2020-06-03",
         day = as.Date(day))
byage0604 = read_csv("./data/data_covid_demo/boros_by_age/boroughs-by-age0604.csv") %>% 
  pivot_longer(BK_CASE_COUNT:SI_DEATH_RATE,
               names_to = "location_n_event",
               values_to = "count")%>% 
  mutate(day = "2020-06-04",
         day = as.Date(day))
byage0605 = read_csv("./data/data_covid_demo/boros_by_age/boroughs-by-age0605.csv") %>% 
  pivot_longer(BK_CASE_COUNT:SI_DEATH_RATE,
               names_to = "location_n_event",
               values_to = "count") %>% 
  mutate(day = "2020-06-05",
         day = as.Date(day))

byage0606 = read_csv("./data/data_covid_demo/boros_by_age/boroughs-by-age0606.csv") %>% 
  pivot_longer(BK_CASE_COUNT:SI_DEATH_RATE,
               names_to = "location_n_event",
               values_to = "count")%>% 
  mutate(day = "2020-06-06",
         day = as.Date(day))
byage0607 = read_csv("./data/data_covid_demo/boros_by_age/boroughs-by-age0607.csv") %>% 
  pivot_longer(BK_CASE_COUNT:SI_DEATH_RATE,
               names_to = "location_n_event",
               values_to = "count")%>% 
  mutate(day = "2020-06-07",
         day = as.Date(day))
byage0608 = read_csv("./data/data_covid_demo/boros_by_age/boroughs-by-age0608.csv") %>% 
  pivot_longer(BK_CASE_COUNT:SI_DEATH_RATE,
               names_to = "location_n_event",
               values_to = "count")%>% 
  mutate(day = "2020-06-08",
         day = as.Date(day))
byage0609 = read_csv("./data/data_covid_demo/boros_by_age/boroughs-by-age0609.csv") %>% 
  pivot_longer(BK_CASE_COUNT:SI_DEATH_RATE,
               names_to = "location_n_event",
               values_to = "count")%>% 
  mutate(day = "2020-06-09",
         day = as.Date(day))

byage0610 = read_csv("./data/data_covid_demo/boros_by_age/boroughs-by-age0610.csv") %>% 
  pivot_longer(BK_CASE_COUNT:SI_DEATH_RATE,
               names_to = "location_n_event",
               values_to = "count")%>% 
  mutate(day = "2020-06-10",
         day = as.Date(day))
byage0611 = read_csv("./data/data_covid_demo/boros_by_age/boroughs-by-age0611.csv") %>% 
  pivot_longer(BK_CASE_COUNT:SI_DEATH_RATE,
               names_to = "location_n_event",
               values_to = "count")%>% 
  mutate(day = "2020-06-11",
         day = as.Date(day))
byage0612 = read_csv("./data/data_covid_demo/boros_by_age/boroughs-by-age0612.csv") %>% 
  pivot_longer(BK_CASE_COUNT:SI_DEATH_RATE,
               names_to = "location_n_event",
               values_to = "count")%>% 
  mutate(day = "2020-06-12",
         day = as.Date(day))
byage0613 = read_csv("./data/data_covid_demo/boros_by_age/boroughs-by-age0613.csv") %>% 
  pivot_longer(BK_CASE_COUNT:SI_DEATH_RATE,
               names_to = "location_n_event",
               values_to = "count")%>% 
  mutate(day = "2020-06-13",
         day = as.Date(day))
byage0614 = read_csv("./data/data_covid_demo/boros_by_age/boroughs-by-age0614.csv") %>% 
  pivot_longer(BK_CASE_COUNT:SI_DEATH_RATE,
               names_to = "location_n_event",
               values_to = "count")%>% 
  mutate(day = "2020-06-14",
         day = as.Date(day))

byage0615 = read_csv("./data/data_covid_demo/boros_by_age/boroughs-by-age0615.csv") %>% 
  pivot_longer(BK_CASE_COUNT:SI_DEATH_RATE,
               names_to = "location_n_event",
               values_to = "count")%>% 
  mutate(day = "2020-06-15",
         day = as.Date(day))
byage0616 = read_csv("./data/data_covid_demo/boros_by_age/boroughs-by-age0616.csv") %>% 
  pivot_longer(BK_CASE_COUNT:SI_DEATH_RATE,
               names_to = "location_n_event",
               values_to = "count")%>% 
  mutate(day = "2020-06-16",
         day = as.Date(day))
byage0617 = read_csv("./data/data_covid_demo/boros_by_age/boroughs-by-age0617.csv") %>% 
  pivot_longer(BK_CASE_COUNT:SI_DEATH_RATE,
               names_to = "location_n_event",
               values_to = "count")%>% 
  mutate(day = "2020-06-17",
         day = as.Date(day))


byage0618 = read_csv("./data/data_covid_demo/boros_by_age/boroughs-by-age0618.csv") %>% 
  pivot_longer(BK_CASE_COUNT:SI_DEATH_RATE,
               names_to = "location_n_event",
               values_to = "count")%>% 
  mutate(day = "2020-06-18",
         day = as.Date(day))
byage0619 = read_csv("./data/data_covid_demo/boros_by_age/boroughs-by-age0619.csv") %>% 
  pivot_longer(BK_CASE_COUNT:SI_DEATH_RATE,
               names_to = "location_n_event",
               values_to = "count")%>% 
  mutate(day = "2020-06-19",
         day = as.Date(day))
byage0620 = read_csv("./data/data_covid_demo/boros_by_age/boroughs-by-age0620.csv") %>% 
  pivot_longer(BK_CASE_COUNT:SI_DEATH_RATE,
               names_to = "location_n_event",
               values_to = "count")%>% 
  mutate(day = "2020-06-20",
         day = as.Date(day))


byage0621 = read_csv("./data/data_covid_demo/boros_by_age/boroughs-by-age0621.csv") %>% 
  pivot_longer(BK_CASE_COUNT:SI_DEATH_RATE,
               names_to = "location_n_event",
               values_to = "count")%>% 
  mutate(day = "2020-06-21",
         day = as.Date(day))
byage0622 = read_csv("./data/data_covid_demo/boros_by_age/boroughs-by-age0622.csv") %>% 
  pivot_longer(BK_CASE_COUNT:SI_DEATH_RATE,
               names_to = "location_n_event",
               values_to = "count")%>% 
  mutate(day = "2020-06-22",
         day = as.Date(day))
byage0623 = read_csv("./data/data_covid_demo/boros_by_age/boroughs-by-age0623.csv") %>% 
  pivot_longer(BK_CASE_COUNT:SI_DEATH_RATE,
               names_to = "location_n_event",
               values_to = "count")%>% 
  mutate(day = "2020-06-23",
         day = as.Date(day))

byage0624 = read_csv("./data/data_covid_demo/boros_by_age/boroughs-by-age0624.csv") %>% 
  pivot_longer(BK_CASE_COUNT:SI_DEATH_RATE,
               names_to = "location_n_event",
               values_to = "count")%>% 
  mutate(day = "2020-06-24",
         day = as.Date(day))
byage0625 = read_csv("./data/data_covid_demo/boros_by_age/boroughs-by-age0625.csv") %>% 
  pivot_longer(BK_CASE_COUNT:SI_DEATH_RATE,
               names_to = "location_n_event",
               values_to = "count")%>% 
  mutate(day = "2020-06-25",
         day = as.Date(day))
byage0626 = read_csv("./data/data_covid_demo/boros_by_age/boroughs-by-age0626.csv") %>% 
  pivot_longer(BK_CASE_COUNT:SI_DEATH_RATE,
               names_to = "location_n_event",
               values_to = "count")%>% 
  mutate(day = "2020-06-26",
         day = as.Date(day))

byage0627 = read_csv("./data/data_covid_demo/boros_by_age/boroughs-by-age0627.csv") %>% 
  pivot_longer(BK_CASE_COUNT:SI_DEATH_RATE,
               names_to = "location_n_event",
               values_to = "count")%>% 
  mutate(day = "2020-06-27",
         day = as.Date(day))

byage0628 = read_csv("./data/data_covid_demo/boros_by_age/boroughs-by-age0628.csv") %>% 
  pivot_longer(BK_CASE_COUNT:SI_DEATH_RATE,
               names_to = "location_n_event",
               values_to = "count")%>% 
  mutate(day = "2020-06-28",
         day = as.Date(day))

byage0630 = read_csv("./data/data_covid_demo/boros_by_age/boroughs-by-age0630.csv") %>% 
  pivot_longer(BK_CASE_COUNT:SI_DEATH_RATE,
               names_to = "location_n_event",
               values_to = "count")%>% 
  mutate(day = "2020-06-30",
         day = as.Date(day))

byage0701 = read_csv("./data/data_covid_demo/boros_by_age/boroughs-by-age0701.csv") %>% 
  pivot_longer(BK_CASE_COUNT:SI_DEATH_RATE,
               names_to = "location_n_event",
               values_to = "count")%>% 
  mutate(day = "2020-07-01",
         day = as.Date(day))

byage0702 = read_csv("./data/data_covid_demo/boros_by_age/boroughs-by-age0702.csv") %>% 
  pivot_longer(BK_CASE_COUNT:SI_DEATH_RATE,
               names_to = "location_n_event",
               values_to = "count")%>% 
  mutate(day = "2020-07-02",
         day = as.Date(day))

byage0703 = read_csv("./data/data_covid_demo/boros_by_age/boroughs-by-age0703.csv") %>% 
  pivot_longer(BK_CASE_COUNT:SI_DEATH_RATE,
               names_to = "location_n_event",
               values_to = "count")%>% 
  mutate(day = "2020-07-03",
         day = as.Date(day))

byage0704 = read_csv("./data/data_covid_demo/boros_by_age/boroughs-by-age0704.csv") %>% 
  pivot_longer(BK_CASE_COUNT:SI_DEATH_RATE,
               names_to = "location_n_event",
               values_to = "count")%>% 
  mutate(day = "2020-07-04",
         day = as.Date(day))

byage0705 = read_csv("./data/data_covid_demo/boros_by_age/boroughs-by-age0705.csv") %>% 
  pivot_longer(BK_CASE_COUNT:SI_DEATH_RATE,
               names_to = "location_n_event",
               values_to = "count")%>% 
  mutate(day = "2020-07-05",
         day = as.Date(day))

byage0705 = read_csv("./data/data_covid_demo/boros_by_age/boroughs-by-age0705.csv") %>% 
  pivot_longer(BK_CASE_COUNT:SI_DEATH_RATE,
               names_to = "location_n_event",
               values_to = "count")%>% 
  mutate(day = "2020-07-05",
         day = as.Date(day))
byage0706 = read_csv("./data/data_covid_demo/boros_by_age/boroughs-by-age0706.csv") %>% 
  pivot_longer(BK_CASE_COUNT:SI_DEATH_RATE,
               names_to = "location_n_event",
               values_to = "count")%>% 
  mutate(day = "2020-07-06",
         day = as.Date(day))

byage0707 = read_csv("./data/data_covid_demo/boros_by_age/boroughs-by-age0707.csv") %>% 
  pivot_longer(BK_CASE_COUNT:SI_DEATH_RATE,
               names_to = "location_n_event",
               values_to = "count")%>% 
  mutate(day = "2020-07-07",
         day = as.Date(day))

byage0708 = read_csv("./data/data_covid_demo/boros_by_age/boroughs-by-age0708.csv") %>% 
  pivot_longer(BK_CASE_COUNT:SI_DEATH_RATE,
               names_to = "location_n_event",
               values_to = "count")%>% 
  mutate(day = "2020-07-08",
         day = as.Date(day))
byage0709 = read_csv("./data/data_covid_demo/boros_by_age/boroughs-by-age0709.csv") %>% 
  pivot_longer(BK_CASE_COUNT:SI_DEATH_RATE,
               names_to = "location_n_event",
               values_to = "count")%>% 
  mutate(day = "2020-07-09",
         day = as.Date(day))

byage0710 = read_csv("./data/data_covid_demo/boros_by_age/boroughs-by-age0710.csv") %>% 
  pivot_longer(BK_CASE_COUNT:SI_DEATH_RATE,
               names_to = "location_n_event",
               values_to = "count")%>% 
  mutate(day = "2020-07-10",
         day = as.Date(day))

byage0711 = read_csv("./data/data_covid_demo/boros_by_age/boroughs-by-age0711.csv") %>% 
  pivot_longer(BK_CASE_COUNT:SI_DEATH_RATE,
               names_to = "location_n_event",
               values_to = "count")%>% 
  mutate(day = "2020-07-11",
         day = as.Date(day))
byage0712 = read_csv("./data/data_covid_demo/boros_by_age/boroughs-by-age0712.csv") %>% 
  pivot_longer(BK_CASE_COUNT:SI_DEATH_RATE,
               names_to = "location_n_event",
               values_to = "count")%>% 
  mutate(day = "2020-07-12",
         day = as.Date(day))

byage0713 = read_csv("./data/data_covid_demo/boros_by_age/boroughs-by-age0713.csv") %>% 
  pivot_longer(BK_CASE_COUNT:SI_DEATH_RATE,
               names_to = "location_n_event",
               values_to = "count")%>% 
  mutate(day = "2020-07-13",
         day = as.Date(day))

byage0714 = read_csv("./data/data_covid_demo/boros_by_age/boroughs-by-age0714.csv") %>% 
  pivot_longer(BK_CASE_COUNT:SI_DEATH_RATE,
               names_to = "location_n_event",
               values_to = "count")%>% 
  mutate(day = "2020-07-14",
         day = as.Date(day))
```

```{r,include=FALSE,message=FALSE,warning=FALSE}
byage = rbind(byage0518,byage0519)
byage = rbind(byage,byage0520)
byage = rbind(byage,byage0521)
byage = rbind(byage,byage0522)
byage = rbind(byage,byage0523)
byage = rbind(byage,byage0524)
byage = rbind(byage,byage0525)
byage = rbind(byage,byage0526)
byage = rbind(byage,byage0527)
byage = rbind(byage,byage0528)
byage = rbind(byage,byage0529)
byage = rbind(byage,byage0530)
byage = rbind(byage,byage0531)
byage = rbind(byage,byage0601)
byage = rbind(byage,byage0602)
byage = rbind(byage,byage0603)
byage = rbind(byage,byage0604)
byage = rbind(byage,byage0605)
byage = rbind(byage,byage0606)
byage = rbind(byage,byage0607)
byage = rbind(byage,byage0608)
byage = rbind(byage,byage0609)
byage = rbind(byage,byage0610)
byage = rbind(byage,byage0611)
byage = rbind(byage,byage0612)
byage = rbind(byage,byage0613)
byage = rbind(byage,byage0614)
byage = rbind(byage,byage0615)
byage = rbind(byage,byage0616)
byage = rbind(byage,byage0617)
byage = rbind(byage,byage0618)
byage = rbind(byage,byage0619)
byage = rbind(byage,byage0620)
byage = rbind(byage,byage0621)
byage = rbind(byage,byage0622)
byage = rbind(byage,byage0623)
byage = rbind(byage,byage0624)
byage = rbind(byage,byage0625)
byage = rbind(byage,byage0626)
byage = rbind(byage,byage0627)
byage = rbind(byage,byage0628)

byage = rbind(byage,byage0630)
byage = rbind(byage,byage0701)
byage = rbind(byage,byage0702)
byage = rbind(byage,byage0703)
byage = rbind(byage,byage0704)
byage = rbind(byage,byage0705)
byage = rbind(byage,byage0706)
byage = rbind(byage,byage0707)
byage = rbind(byage,byage0708)
byage = rbind(byage,byage0709)
byage = rbind(byage,byage0710)
byage = rbind(byage,byage0711)
byage = rbind(byage,byage0712)
byage = rbind(byage,byage0713)
byage = rbind(byage,byage0714)
```


```{r,include=FALSE,message=FALSE,warning=FALSE}
byage = byage %>% separate(location_n_event,
                   into = c("location","outcome"),sep = 3) %>% 
  separate(location, into = c("boro", "x"),sep = 2) %>% 
  dplyr:: select(-x)

#write_csv(byage,"./distribution_of_covid-19/data/demoage_data.csv")

```

After read the data we would clean it (But these code shows in the app.R)
```{r}
byage = read_csv("./distribution_of_covid-19/data/demoage_data.csv") %>% 
  mutate(outcome = str_replace_all(outcome, "CASE_COUNT","Case Count"),
         outcome = str_replace_all(outcome, "HOSPITALIZED_COUNT","Hospitalization Count"),
         outcome = str_replace_all(outcome, "DEATH_COUNT","Death Count"),
         outcome = str_replace_all(outcome, "CASE_RATE","Case Rate (per 100,000 people)"),
         outcome = str_replace_all(outcome, "HOSPITALIZED_RATE","Hospitalization Rate (per 100,000 people)"),
         outcome = str_replace_all(outcome, "DEATH_RATE","Death Rate (per 100,000 people)"),
         boro = str_replace_all(boro, "BK","Brooklyn"),
         boro = str_replace_all(boro, "MN","Manhattan"),
         boro = str_replace_all(boro, "QN","Queens"),
         boro = str_replace_all(boro, "BX","Bronx"),
         boro = str_replace_all(boro, "SI","Staten Island"),
         count = round(count))
```



## Trends

We already have the data of April, May and June. I combined them together.

June as the example
### The first plot
Use this data.
https://github.com/nychealth/coronavirus-data/blob/master/case-hosp-death.csv


### The ZCTA level plot (The second plot)
```{r}

data0601 = read.csv("./data/June/0601/data-by-modzcta0601.csv") %>% 
  drop_na()%>% janitor::clean_names() %>% 
  rename(positive = covid_case_count,
         zipcode = modified_zcta) %>% 
  mutate(day = "2020-06-01",
         day = as.Date(day))

data0602 = read.csv("./data/June/0602/data-by-modzcta0602.csv") %>% 
  drop_na()%>% janitor::clean_names() %>% 
  rename(positive = covid_case_count,
         zipcode = modified_zcta) %>% 
  mutate(day = "2020-06-02",
         day = as.Date(day))

data0603 = read.csv("./data/June/0603/data-by-modzcta0603.csv") %>% 
  drop_na()%>% janitor::clean_names() %>% 
  rename(positive = covid_case_count,
         zipcode = modified_zcta) %>% 
  mutate(day = "2020-06-03",
         day = as.Date(day))

data0604 = read.csv("./data/June/0604/data-by-modzcta0604.csv") %>% 
  drop_na()%>% janitor::clean_names() %>% 
  rename(positive = covid_case_count,
         zipcode = modified_zcta) %>% 
  mutate(day = "2020-06-04",
         day = as.Date(day))

data0605 = read.csv("./data/June/0605/data-by-modzcta0605.csv") %>% 
  drop_na()%>% janitor::clean_names() %>% 
  rename(positive = covid_case_count,
         zipcode = modified_zcta) %>% 
  mutate(day = "2020-06-05",
         day = as.Date(day))

data0606 = read.csv("./data/June/0606/data-by-modzcta0606.csv") %>% 
  drop_na()%>% janitor::clean_names() %>% 
  rename(positive = covid_case_count,
         zipcode = modified_zcta) %>% 
  mutate(day = "2020-06-06",
         day = as.Date(day))

data0607 = read.csv("./data/June/0607/data-by-modzcta0607.csv") %>% 
  drop_na()%>% janitor::clean_names() %>% 
  rename(positive = covid_case_count,
         zipcode = modified_zcta) %>% 
  mutate(day = "2020-06-07",
         day = as.Date(day))

data0608 = read.csv("./data/June/0608/data-by-modzcta0608.csv") %>% 
  drop_na()%>% janitor::clean_names() %>% 
  rename(positive = covid_case_count,
         zipcode = modified_zcta) %>% 
  mutate(day = "2020-06-08",
         day = as.Date(day))

data0609 = read.csv("./data/June/0609/data-by-modzcta0609.csv") %>% 
  drop_na()%>% janitor::clean_names() %>% 
  rename(positive = covid_case_count,
         zipcode = modified_zcta) %>% 
  mutate(day = "2020-06-09",
         day = as.Date(day))

data0610 = read.csv("./data/June/0610/data-by-modzcta0610.csv") %>% 
  drop_na()%>% janitor::clean_names() %>% 
  rename(positive = covid_case_count,
         zipcode = modified_zcta) %>% 
  mutate(day = "2020-06-10",
         day = as.Date(day))

data0611 = read.csv("./data/June/0611/data-by-modzcta0611.csv") %>% 
  drop_na()%>% janitor::clean_names() %>% 
  rename(positive = covid_case_count,
         zipcode = modified_zcta) %>% 
  mutate(day = "2020-06-11",
         day = as.Date(day))

data0612 = read.csv("./data/June/0612/data-by-modzcta0612.csv") %>% 
  drop_na()%>% janitor::clean_names() %>% 
  rename(positive = covid_case_count,
         zipcode = modified_zcta) %>% 
  mutate(day = "2020-06-12",
         day = as.Date(day))

data0613 = read.csv("./data/June/0613/data-by-modzcta0613.csv") %>% 
  drop_na()%>% janitor::clean_names() %>% 
  rename(positive = covid_case_count,
         zipcode = modified_zcta) %>% 
  mutate(day = "2020-06-13",
         day = as.Date(day))

data0614 = read.csv("./data/June/0614/data-by-modzcta0614.csv") %>% 
  drop_na()%>% janitor::clean_names() %>% 
  rename(positive = covid_case_count,
         zipcode = modified_zcta) %>% 
  mutate(day = "2020-06-14",
         day = as.Date(day))

data0615 = read.csv("./data/June/0615/data-by-modzcta0615.csv") %>% 
  drop_na()%>% janitor::clean_names() %>% 
  rename(positive = covid_case_count,
         zipcode = modified_zcta) %>% 
  mutate(day = "2020-06-15",
         day = as.Date(day))

data0616 = read.csv("./data/June/0616/data-by-modzcta0616.csv") %>% 
  drop_na()%>% janitor::clean_names() %>% 
  rename(positive = covid_case_count,
         zipcode = modified_zcta) %>% 
  mutate(day = "2020-06-16",
         day = as.Date(day))
data0617 = read.csv("./data/June/0617/data-by-modzcta0617.csv") %>% 
  drop_na()%>% janitor::clean_names() %>% 
  rename(positive = covid_case_count,
         zipcode = modified_zcta) %>% 
  mutate(day = "2020-06-17",
         day = as.Date(day))
data0618 = read.csv("./data/June/0618/data-by-modzcta0618.csv") %>% 
  drop_na()%>% janitor::clean_names() %>% 
  rename(positive = covid_case_count,
         zipcode = modified_zcta) %>% 
  mutate(day = "2020-06-18",
         day = as.Date(day))

data0619 = read.csv("./data/June/0619/data-by-modzcta0619.csv") %>% 
  drop_na()%>% janitor::clean_names() %>% 
  rename(positive = covid_case_count,
         zipcode = modified_zcta) %>% 
  mutate(day = "2020-06-19",
         day = as.Date(day))
data0620 = read.csv("./data/June/0620/data-by-modzcta0620.csv") %>% 
  drop_na()%>% janitor::clean_names() %>% 
  rename(positive = covid_case_count,
         zipcode = modified_zcta) %>% 
  mutate(day = "2020-06-20",
         day = as.Date(day))

data0621 = read.csv("./data/June/0621/data-by-modzcta0621.csv") %>% 
  drop_na()%>% janitor::clean_names() %>% 
  rename(positive = covid_case_count,
         zipcode = modified_zcta) %>% 
  mutate(day = "2020-06-21",
         day = as.Date(day))
data0622 = read.csv("./data/June/0622/data-by-modzcta0622.csv") %>% 
  drop_na()%>% janitor::clean_names() %>% 
  rename(positive = covid_case_count,
         zipcode = modified_zcta) %>% 
  mutate(day = "2020-06-22",
         day = as.Date(day))

data0623 = read.csv("./data/June/0623/data-by-modzcta0623.csv") %>% 
  drop_na()%>% janitor::clean_names() %>% 
  rename(positive = covid_case_count,
         zipcode = modified_zcta) %>% 
  mutate(day = "2020-06-23",
         day = as.Date(day))

data0624 = read.csv("./data/June/0624/data-by-modzcta0624.csv") %>% 
  drop_na()%>% janitor::clean_names() %>% 
  rename(positive = covid_case_count,
         zipcode = modified_zcta) %>% 
  mutate(day = "2020-06-24",
         day = as.Date(day))
data0625 = read.csv("./data/June/0625/data-by-modzcta0625.csv") %>% 
  drop_na()%>% janitor::clean_names() %>% 
  rename(positive = covid_case_count,
         zipcode = modified_zcta) %>% 
  mutate(day = "2020-06-25",
         day = as.Date(day))
data0626 = read.csv("./data/June/0626/data-by-modzcta0626.csv") %>% 
  drop_na()%>% janitor::clean_names() %>% 
  rename(positive = covid_case_count,
         zipcode = modified_zcta) %>% 
  mutate(day = "2020-06-26",
         day = as.Date(day))
data0627 = read.csv("./data/June/0627/data-by-modzcta0627.csv") %>% 
  drop_na()%>% janitor::clean_names() %>% 
  rename(positive = covid_case_count,
         zipcode = modified_zcta) %>% 
  mutate(day = "2020-06-27",
         day = as.Date(day))

data0628 = read.csv("./data/June/0628/data-by-modzcta0628.csv") %>% 
  drop_na()%>% janitor::clean_names() %>% 
  rename(positive = covid_case_count,
         zipcode = modified_zcta) %>% 
  mutate(day = "2020-06-28",
         day = as.Date(day))

#there is no 0629 data

data0630 = read.csv("./data/June/0630/data-by-modzcta0630.csv") %>% 
  drop_na()%>% janitor::clean_names() %>% 
  rename(positive = covid_case_count,
         zipcode = modified_zcta) %>% 
  mutate(day = "2020-06-30",
         day = as.Date(day))
```


```{r}
Junedata = full_join(data0601,data0602)
Junedata = full_join(Junedata, data0603)
Junedata = full_join(Junedata, data0604)
Junedata = full_join(Junedata, data0605)
Junedata = full_join(Junedata, data0606)
Junedata = full_join(Junedata, data0607)
Junedata = full_join(Junedata, data0608)
Junedata = full_join(Junedata, data0609)
Junedata = full_join(Junedata, data0610)
Junedata = full_join(Junedata, data0611)
Junedata = full_join(Junedata, data0612)
Junedata = full_join(Junedata, data0613)
Junedata = full_join(Junedata, data0614)
Junedata = full_join(Junedata, data0615)
Junedata = full_join(Junedata, data0616)
Junedata = full_join(Junedata, data0617)
Junedata = full_join(Junedata, data0618)
Junedata = full_join(Junedata, data0619)
Junedata = full_join(Junedata, data0620)
Junedata = full_join(Junedata, data0621)
Junedata = full_join(Junedata, data0622)
Junedata = full_join(Junedata, data0623)
Junedata = full_join(Junedata, data0624)
Junedata = full_join(Junedata, data0625)
Junedata = full_join(Junedata, data0626)
Junedata = full_join(Junedata, data0627)
Junedata = full_join(Junedata, data0628)
Junedata = full_join(Junedata, data0630)


newcases_june= 0
#newcases data clean
for (i in 1:177) {
  newcases_june[i] = 0 
  
  newcases_june
}

for (i in 178:5133) {
  newcases_june[i] = Junedata[i,4] - Junedata[i-177,4]
 
  newcases_june
}

Junedata = Junedata %>% 
  mutate(newcases_june = newcases_june)

# write.csv(Junedata, "/Users/ziqizhou/Desktop/MSPH_1st_Year/P8105_Data_Science/Git/NYC_covid-19.github.io/data/final_Junedata.csv")
```


Trends by demographics also use the byage, bysex, byrace data.

